Only the store can save you now:\\Updates and vulnerabilities on Android

### 2015-04-10 securityupdates.tex
Comment out Acknowledgements during review, we can bring them back for the camera ready

\identifying{
\section*{Acknowledgements}
Thanks to: Richard Clayton, the mobile security reading group, Anil Madhavapeddy and Oliver Chick for reading drafts;
David Robertson for statistical advice;
and Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities.
We were funded by the EPSRC and Google but the the work presented here does not necessarily reflect their views.
}

>>>>

\identifying{
%\section*{Acknowledgements}
%Thanks to: Richard Clayton, the mobile security reading group, Anil Madhavapeddy and Oliver Chick for reading drafts;
%David Robertson for statistical advice;
%and Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting %vulnerabilities.
%We were funded by the EPSRC and Google but the the work presented here does not necessarily reflect their %views.
}
